Final Project Report: Developing an AI-Assisted Grading System Using Large Language Models

### 2025-08-17 FinalProject/src/paper.tex
updatedTesting

% ===================== Packages =====================
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[sc,osf]{mathpazo}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float}        % for [H] placement if desired
\usepackage{tikz}         % Diagrams
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,matrix}
\usepackage{siunitx}      % Optional but useful
\sisetup{detect-all}
\PassOptionsToPackage{hyphens}{url} % Make long URLs break better in refs (must come before hyperref)
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[nameinlink,capitalize,noabbrev]{cleveref}
\usepackage{bookmark}     % better PDF outlines
\usepackage{csquotes}     % for \enquote
\usepackage{tabularx}     % better tables that auto-wrap
\urlstyle{same}
\usepackage{listings}
\usepackage{lstautogobble} % trims common indent
\usepackage{array}
\usepackage{tabularx}
\usepackage{makecell}
\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  breakatwhitespace=true,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  autogobble=true,
  xleftmargin=1ex,
  xrightmargin=1ex,
}

@@

\lstdefinelanguage{yaml}{
  comment=[l]{\#},
  morestring=[b]',
  morestring=[b]"
}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
% --- Safe placeholders + brand names ---
\newcommand{\ph}[1]{\textit{<#1>}} % use like \ph{value}, never triggers math mode
\newcommand{\Brand}[1]{\mbox{#1}}  % keep vendor names from awkward hyphenation

% Colors for links
\definecolor{dark-red}{rgb}{0.6,0,0}
\definecolor{dark-green}{rgb}{0,0.6,0}
\definecolor{dark-blue}{rgb}{0,0,0.6}
\interfootnotelinepenalty=10000 % Prevent breaking footnotes across pages

% Graphics path
\graphicspath{{images/}}

@@

% -----------------------------------------------------------------------------------------------

\chapter{Testing and Evaluation Plan}\label{chap:evalplan}

@@

@@

\section{Evaluation Summary (Aligned to Proposal Tests)}

\section{Final Outcomes and Deliverables}
We delivered the integrated web app, background services, reproducible prompts/model versions, and a grade export flow compatible with LMS import. Documentation includes an instructor guide and technical deployment notes.

\section{Lessons Learned and Future Work}
\begin{compactitem}
  \item Visual pre-processing (downscale/tiling) mattered more for stability than minor prompt tuning.
  \item Instructors preferred neutral group names and an explicit \emph{Ungrouped} bin.
  \item Future: domain-tuned prompts for math diagrams, adaptive thresholding for faint pencil, pre-clustering to cut LLM calls, regrade workflow, and CSV/Excel export automation to specific LMS formats.
\end{compactitem}

@@

\subsection*{Point the callers at \texttt{PythonApi:BaseUrl}}
Update the two callers to use \texttt{PythonApi:BaseUrl} \emph{without} a localhost fallback.

\paragraph{CourseService.cs (snippet)}
\begin{lstlisting}[language={[Sharp]C}]
var client  = _httpClientFactory.CreateClient();
var baseUrl = _configuration.GetValue<string>("PythonApi:BaseUrl");
client.BaseAddress = new Uri(baseUrl);

var response = await client.PostAsJsonAsync("/autogroup", requestBody);
response.EnsureSuccessStatusCode();
\end{lstlisting}

\paragraph{GroupingService.cs (snippet)}
\begin{lstlisting}[language={[Sharp]C}]
var client  = _httpClientFactory.CreateClient();
var baseUrl = _configuration.GetValue<string>("PythonApi:BaseUrl");
client.BaseAddress = new Uri(baseUrl);

// ...status polling / error handling continues...
\end{lstlisting}

>>>>

% ===================== Packages =====================
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[sc,osf]{mathpazo}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float} % for [H] placement if desired
\usepackage{tikz} % Diagrams
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit,matrix}
\usepackage{siunitx} % Optional but useful
\sisetup{detect-all}
\PassOptionsToPackage{hyphens}{url} % Make long URLs break better in refs (must come before hyperref)
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[nameinlink,capitalize,noabbrev]{cleveref}
\usepackage{bookmark} % better PDF outlines
\usepackage{csquotes} % for \enquote
\usepackage{tabularx} % better tables that auto-wrap
\urlstyle{same}
\usepackage{listings}
\usepackage{lstautogobble} % trims common indent
\usepackage{array}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{subcaption} % defines the subfigure environment
\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  breakatwhitespace=false, % Allow breaks anywhere (fixes long strings like connection URLs)
  breakindent=20pt, % Indent wrapped lines for better readability in .cs files
  postbreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\color{gray}\hookrightarrow\space}}, % Subtle continuation arrow for wrapped lines
  columns=fixed, % Changed to fixed for true monospace and even frame lines (prevents uneven extensions)
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  framerule=0.5pt, % Thinner frame rule to reduce visual emphasis on any minor irregularities
  rulecolor=\color{gray}, % Gray frame for subtlety
  framesep=5pt, % Inner padding to keep content from edges
  autogobble=true,
  xleftmargin=5pt, % Slightly wider left margin to prevent hugging
  xrightmargin=5pt, % Matching right margin
  tabsize=4 % Standardize tabs (fixes potential "weird" alignment in .cs code)
}

@@

\lstdefinelanguage{yaml}{
  comment=[l]{\#},
  morestring=[b]',
  morestring=[b]"
}
% C# language definition for better syntax handling
\lstdefinelanguage{CSharp}{
  morekeywords={abstract, as, base, bool, break, byte, case, catch, char, checked, class, const, continue, decimal, default, delegate, do, double, else, enum, event, explicit, extern, false, finally, fixed, float, for, foreach, goto, if, implicit, in, int, interface, internal, is, lock, long, namespace, new, null, object, operator, out, override, params, private, protected, public, readonly, ref, return, sbyte, sealed, short, sizeof, stackalloc, static, string, struct, switch, this, throw, true, try, typeof, uint, ulong, unchecked, unsafe, ushort, using, virtual, void, volatile, while},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  literate=
   *{0}{{{\color{black}0}}}{1}
    {1}{{{\color{black}1}}}{1}
    {2}{{{\color{black}2}}}{1}
    {3}{{{\color{black}3}}}{1}
    {4}{{{\color{black}4}}}{1}
    {5}{{{\color{black}5}}}{1}
    {6}{{{\color{black}6}}}{1}
    {7}{{{\color{black}7}}}{1}
    {8}{{{\color{black}8}}}{1}
    {9}{{{\color{black}9}}}{1},
}
\lstset{
  language=CSharp,  % Set default to CSharp for .cs files
  keywordstyle=\color{blue}\bfseries,
  commentstyle=\color{green!60!black},
  stringstyle=\color{red},
  numbers=none % Remove line numbers to match original setup and avoid extra left space that could offset frames
}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
% --- Safe placeholders + brand names ---
\newcommand{\ph}[1]{\textit{<#1>}} % use like \ph{value}, never triggers math mode
\newcommand{\Brand}[1]{\mbox{#1}} % keep vendor names from awkward hyphenation
% Colors for links
\definecolor{dark-red}{rgb}{0.6,0,0}
\definecolor{dark-green}{rgb}{0,0.6,0}
\definecolor{dark-blue}{rgb}{0,0,0.6}
\interfootnotelinepenalty=10000 % Prevent breaking footnotes across pages
% --- SAFE MaybeImage macro (replaces the old one) ---
\newcommand{\MaybeImage}[2][\linewidth]{%
\begingroup
\def\imgA{#2}%
\def\imgB{images/#2}%
\IfFileExists{\imgA}{%
\includegraphics[width=#1]{\imgA}%
  }{%
\IfFileExists{\imgB}{%
\includegraphics[width=#1]{\imgB}%
    }{%
\fbox{%
\parbox[c][0.25\textheight][c]{#1}{\centering
\small Placeholder (file missing)\\[2pt]\texttt{\detokenize{#2}}\\[2pt]
          Add this image to \texttt{images/}}
      }%
    }%
  }%
\endgroup
}
% Graphics path
\graphicspath{{images/}}

@@

% --------------------------------------------------------------------------------
\chapter{Testing and Evaluation Plan}\label{chap:evalplan}

\section{Objectives}
We will provide concise, visual evidence that the system:
(i) processes submissions end-to-end,
(ii) groups answer \emph{images} by semantic similarity (no answer OCR),
(iii) isolates outliers for review,
(iv) applies rubrics and propagates score changes consistently, and
(v) supports clipboard-based grade transfer (\emph{Copy Table}) into external systems.

\section{Test Data}
A small gold-labeled set (12–20 pages) mixing typed and handwritten responses.
Known-correct exemplars are used only to \emph{interpret} cluster coherence; the system does not OCR answer content.

\section{Planned Tests \& Evidence}
\textbf{A. Basic Flow.} Upload \(\rightarrow\) process \(\rightarrow\) results; rubric application updates totals.  
\emph{Evidence:} one multi-panel figure combining upload/process, results view, and rubric before/after.

\textbf{B. Vision-Based Semantic Recognition (No Answer OCR).}
GPT-4o Vision groups answer \emph{images} by meaning.  
\emph{Evidence:} one compact figure with (a) Cluster~A gallery (similar idea), (b) Cluster~B gallery (different idea), and (c) Outliers gallery (heterogeneous/suspect).

\textbf{C. Rubric Propagation \& Clipboard Interop.}
Totals update after a rubric edit; the on-screen grade table can be copied to the clipboard and pasted into an LMS/spreadsheet.  
\emph{Evidence:} a figure showing the \emph{Copy Table} UI and the pasted result.

\section{Execution (Concise)}
(1) Upload a multi-page PDF and capture upload/process. 
(2) Open a representative question and capture results.
(3) Apply a rubric item and capture before/after.
(4) Capture Cluster~A, Cluster~B, and Outliers as tiled galleries;
(5) Use \emph{Copy Table}; paste into a spreadsheet or LMS text area; capture both the source table and the pasted result.

\section{Acceptance (Visual)}
An end-to-end success notice; coherent clusters with visually similar answers grouped together; clear outlier separation; visible rubric propagation; and successful clipboard transfer of grades (rows/columns preserved) into an external target.

@@

\section{Basic Flow and Rubric Application}
Figure~\ref{fig:basic-flow} shows the end-to-end path from upload to results,
and that applying a rubric immediately updates affected totals.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{basic_upload.png}
    \caption{Upload \& processing complete}
  \end{subfigure}\hfill
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{basic_results.png}
    \caption{Results view (groups \& scores)}
  \end{subfigure}

  \vspace{0.5em}
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{rubric_before.png}
    \caption{Before applying rubric}
  \end{subfigure}\hfill
  \begin{subfigure}{0.49\linewidth}
    \MaybeImage[0.99\linewidth]{rubric_after.png}
    \caption{After applying rubric (totals updated)}
  \end{subfigure}
  \caption{End-to-end processing and rubric application.}
  \label{fig:basic-flow}
\end{figure}

\section{Vision-Based Semantic Grouping (No Answer OCR)}
The system does not OCR answer text; instead, GPT-4o Vision groups \emph{answer crops}
by semantic similarity. Figure~\ref{fig:vision-groups} shows two coherent clusters
and an outlier set. Each gallery tile is a raw answer crop; the visual consistency
within a cluster indicates similar meaning, while the outlier gallery aggregates
heterogeneous or non-matching answers.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.32\linewidth}
    \MaybeImage[0.99\linewidth]{cluster_A_gallery.png}
    \caption{Cluster A (same idea)}
  \end{subfigure}\hfill
  \begin{subfigure}{0.32\linewidth}
    \MaybeImage[0.99\linewidth]{cluster_B_gallery.png}
    \caption{Cluster B (different idea)}
  \end{subfigure}\hfill
  \begin{subfigure}{0.32\linewidth}
    \MaybeImage[0.99\linewidth]{cluster_outliers.png}
    \caption{Outliers (mixed/unclear)}
  \end{subfigure}

  \vspace{0.75em}

  \MaybeImage[0.6\linewidth]{grouping_scatter.png}

  \caption{Vision-led semantic grouping from images only: coherent clusters (left, middle) and outliers (right).}
  \label{fig:vision-groups}
\end{figure}

\section{Rubric Propagation \& Clipboard Interoperability}
After editing a rubric item, totals are recomputed across affected answers.
Rather than exporting a file, instructors click \emph{Copy Table} to copy grades
to the clipboard and then paste into an external system (e.g., LMS gradebook or spreadsheet).
Figure~\ref{fig:copy-table} shows the copyable grade table and the pasted result.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.6\linewidth}
    \MaybeImage[0.99\linewidth]{copy_table.png}
    \caption{Copyable grade table in the app}
  \end{subfigure}

  \vspace{0.5em}
  \begin{subfigure}{0.6\linewidth}
    \MaybeImage[0.99\linewidth]{paste_example.png}
    \caption{Pasted result in a spreadsheet/LMS text area}
  \end{subfigure}
  \caption{Clipboard-based grade transfer using \emph{Copy Table}.}
  \label{fig:copy-table}
\end{figure}

\section{Summary}
Across these compact figures, we visually confirm correct end-to-end processing,
vision-based semantic grouping with isolated outliers,
consistent rubric propagation, and successful clipboard transfer of grades via \emph{Copy Table}.

@@

\section{Evaluation Summary}
Our visual tests demonstrated end-to-end processing, coherent semantic grouping (no answer OCR), consistent rubric propagation, and reliable clipboard-based grade transfer using \emph{Copy Table}.

\section{Final Outcomes and Deliverables}
We delivered the integrated web app, background services, reproducible prompts/model versions, and a \emph{Copy Table} flow that enables fast pasting of grades into external systems (e.g., LMS/Sheets). Documentation includes an instructor guide and technical deployment notes.

\section{Lessons Learned and Future Work}
\begin{compactitem}
  \item Visual pre-processing (downscale/tiling) mattered more for stability than minor prompt tuning.
  \item Instructors preferred neutral group names and an explicit \emph{Ungrouped} bin.
  \item Future: direct CSV/Excel export in addition to \emph{Copy Table}; domain-tuned prompts for math diagrams; adaptive thresholding for faint pencil; pre-clustering to cut LLM calls; regrade workflow.
\end{compactitem}

@@

\subsection*{Point the callers at \texttt{PythonApi:BaseUrl}}
Update the two callers to use \texttt{PythonApi:BaseUrl} \emph{without} a localhost fallback.
\noindent
\begin{minipage}{\linewidth}
\begin{lstlisting}[language=CSharp,title=CourseService.cs (snippet)]
var client = _httpClientFactory.CreateClient();
var baseUrl = _configuration.GetValue<string>("PythonApi:BaseUrl");
client.BaseAddress = new Uri(baseUrl);

var response = await client.PostAsJsonAsync("/autogroup", requestBody);
response.EnsureSuccessStatusCode();
\end{lstlisting}
\end{minipage}
\noindent
\begin{minipage}{\linewidth}
\begin{lstlisting}[language=CSharp,title=GroupingService.cs (snippet)]
var client = _httpClientFactory.CreateClient();
var baseUrl = _configuration.GetValue<string>("PythonApi:BaseUrl");
client.BaseAddress = new Uri(baseUrl);

// ...status polling / error handling continues...
\end{lstlisting}
\end{minipage}
